### 2020-04-01 writeup/setup.tex
edits

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
	\item {\bf Negative transfer from model shift:} we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
\end{enumerate}

>>>>

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
	\item {\bf Negative transfer from model shift:} we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
\end{enumerate}

Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediciton labels/tasks for every image \cite{EA20}.
\todo{We show the following results.}
